Optimizing httk's 3comp2 model

### 2025-06-02 data-raw/optimizing_httk_model.Rmd
Fixing total liver flow, renal and hepatic clearance definition in 1comp_cl model functions. Added liver_mass as a parameter to facilitate hepatic clearance calculations.

```{r}
test_pk <- pk(data = minicvt) + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  stat_model(model = c("model_flat", "model_1comp_cl_rest",
                       "model_1comp_cl_nonrest", "model_1comp_fup")) +
  settings_optimx(hessian = TRUE) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE)

@@

test_pk$prefit$par_DF |> View()

test_fit <- do_fit(test_pk, n_cores = 8)
winmodel <- get_winning_model(test_fit)
View(winmodel)
winmodel %>% ungroup() %>% count(method, model)
get_fit(test_fit) %>%
  filter(convcode == 0) %>%
  ungroup() %>%
  distinct(Chemical, Species, model, method) %>% View()

pl <- plot(test_fit, use_scale_conc = TRUE,best_fit = FALSE, log10_C = TRUE,
           method = "bobyqa", fit_limits = 10)
pl %>%
  filter(Chemical == "DTXSID0020442") %>%
  pull(final_plot) %>% .[[1]]

@@

>>>>

```{r}
test_pk <- pk(data = minicvt) + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  stat_model(model = c("model_flat", "model_1comp_cl_rest",
                       "model_1comp_cl_nonrest", "model_1comp_fup")) +
  settings_optimx(hessian = TRUE) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE)

@@

test_fit <- do_fit(test_pk, n_cores = 4)
winmodel <- get_winning_model(test_fit)
winmodel %>% ungroup() %>% count(method, model)
View(winmodel)
get_fit(test_fit) %>%
  filter(convcode == 0) %>%
  ungroup() %>%
  distinct(Chemical, Species, model, method) %>% View()

pl <- plot(test_fit, use_scale_conc = FALSE,
           best_fit = FALSE, log10_C = FALSE,
           method = "L-BFGS-B")

winmodel %>%
  filter(model != "model_flat") %>%
  distinct(Chemical, model)

pl %>%
  filter(Chemical == "DTXSID0020442") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID2020139") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID4020458") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID4022527") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID4032405") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID5023320") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID6022923") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID7046627") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID8020541") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID8032673") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID9020584") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID9032329") %>%
  pull(final_plot) %>% .[[1]]

@@

get_fit(test_fit) %>%
  semi_join(winmodel) %>%
  filter(model != "model_flat", optimize_param) %>%
  mutate(diff_est = estimate - start) %>%
  View("diffs")

get_fit(test_fit) %>%
  semi_join(winmodel) %>%
  filter(model != "model_flat", optimize_param,
         convcode == 0) %>%
  mutate(diff_est = estimate - start) %>%
  filter(stringr::str_detect(param_name, "sigma_", negate = TRUE)) %>%
  group_by(model, method, param_name) %>%
  summarize(avg_diff = mean(diff_est),
            min_diff = min(diff_est),
            max_diff = max(diff_est))
